An Investigation in Topological Properties

### 2018-05-03 article.tex
Corrections and Bibliography

	\begin{theorem}
		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
	\end{theorem}
	\begin{proof} 
	This was not finished correctly and fell through the cracks of time. Should it be removed?
	\end{proof}

@@

	\begin{theorem}
	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
	\end{theorem}
	\begin{proof}:\newline
		\begin{enumerate}
		\item Let $\mathcal{B} = \lbrace (a, b) : a < b \in \mathbb{Q}\rbrace$ Let $x \in \mathbb{R}$ then, $\lfloor x \rfloor -1 < x < \lceil x \rceil + 1$. Let B = $(\lfloor x \rfloor -1, \lceil x \rceil + 1)$, so $x \in B \in \mathcal{B}$ and $B \subseteq \mathbb{Q}$.
		\item Now, for $B_1, B_2 \in \mathcal{B}, \exists x \in B_1 \cap B_2 : x \in B_1$ and $x \in B_2$. $a_1, a_2 < b_1, b_2 \in \mathbb{Q}.$ Let $B_1 = (a_1, b_1)$ and $B_2 = (a_2, b_2)$. Now let $B_3 = (max(a_1,a_2), min(b_1,b_2))$ with $a_1,a_2<x<b_1,b_2$ so $x \in B_3$. So, $x \in B_3 \subseteq B_1 \cap B_2$.
		\item Now show it generates $\tau$...
		\end{enumerate} 
	\end{proof}

\section{Compactness Properties}

@@

	\begin{theorem}
		Every \textbf{hemicompact} subset of a topological space is \(\boldsymbol{\sigma}\)\textbf{-compact}.
	\end{theorem}
	\begin{proof}
		Let $K_n \subseteq K$ witness hemicompactness, of course $\underset{n \in \mathbb{N}}{\bigcup}K_n \subseteq K$, since $K_n \subseteq K$. Let $k \in K$, so $\lbrace k \rbrace$ is compact and $\bigcup\lbrace k \rbrace = K$. For $k_n \in K$, choose $K_n : k_n \in K_n \subseteq K$, so $K = \underset{n \in \mathbb{N}}{\bigcup}K_n$
	\end{proof}

@@

	\begin{theorem}
		If $X$ is \textbf{Lindel\"of} and locally compact, then $\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)}$
	\end{theorem}
	\begin{proof}
		For $x \in X$, let $x \in U_x \subseteq K_x$ for $U_x$ open and $K_x$ compact. Then by definition of Lindel\"of choose $U_n \in \mathcal{U} = \lbrace U_x : x \in X \rbrace$ such that $\underset{n \in \mathbb{N}}{\bigcup}U_n = X$. Then for each $U_n$, there exists compact $K_n$ where $U_n \subseteq K_n$. \newline
		For $Gru_{\mathcal{K}, \mathcal{P}} (X)$, let $\sigma(n) = K_n$ denote a strategy for $\mathcal{K}$, $\mathcal{K}$ chooses compact $K_n \supseteq U_n \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in K_n$. $\lbrace K_i : i < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$. For $\mathcal{P}$ to win, there must be $U_n \in \mathcal{C}$ such that $\sigma(n) \not\supseteq U_n$, but we've already established that $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$ so contradiction, thus $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
	\end{proof}

	\begin{theorem}
		$\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)} \Rightarrow X$ is \textbf{hemicompact}.
	\end{theorem}
	\begin{proof}
		We prove the contrapositive. Let $\sigma$ be a predetermined strategy, and assume $X$ isn't hemicompact. So there exists a compact $K$ that isn't a union of finite $\sigma(n)$, so player $\mathcal{P}$ may always legally choose a point $p_n \in K$. Then by the lemma, $\langle p_n \rangle$ has a cluster point. Therefore $\sigma$ isn't a winning strategy.
	\end{proof}
\end{document}

>>>>

	\begin{proposition}
		The ``topology generated by \(\mathcal{B}\)'' is actually a topology.
	\end{proposition}

@@

	\begin{proposition}
	$\lbrace($a, b$)$ : a $<$ b $\in \mathbb{Q}\rbrace$ is a basis for the Euclidean topology.
	\end{proposition}

\section{Covering Properties}

@@

	\begin{theorem}
		Every \textbf{hemicompact} subset of a topological space is \(\boldsymbol{\sigma}\)\textbf{-compact}.
	\end{theorem}
	\begin{proof}
		Let $K_n \subseteq K$ witness hemicompactness, of course $\underset{n \in \mathbb{N}}{\bigcup}K_n \subseteq K$, since $K_n \subseteq K$. Let $k \in K$, so $\lbrace k \rbrace$ it compact, thus there is some $n \in \mathbb{N}$ such that $\lbrace k \rbrace \subseteq K_n$. Therefore $k \in K_n \subseteq K$, so $K = \underset{n \in \mathbb{N}}{\bigcup}K_n$.
	\end{proof}

@@

	\begin{theorem}
		If $X$ is \textbf{Lindel\"of} and locally compact, then $\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)}$
	\end{theorem}
	\begin{proof}
		For $x \in X$, let $x \in U_x \subseteq K_x$ for $U_x$ open and $K_x$ compact. Then by definition of Lindel\"of choose $U_n \in \mathcal{U} = \lbrace U_x : x \in X \rbrace$ such that $\underset{n \in \mathbb{N}}{\bigcup}U_n = X$. Then for each $U_n$, there exists compact $K_n$ where $U_n \subseteq K_n$. \newline
		For $Gru_{\mathcal{K}, \mathcal{P}} (X)$, let $\sigma(n) = K_n$ denote a strategy for $\mathcal{K}$, $\mathcal{K}$ chooses compact $K_n \supseteq U_n \in \mathcal{C}$ and $\mathcal{P}$ chooses $p \in X$ such that $p \not\in \underset{m \leq n}{\bigcup}K_m$. $\lbrace K_i : i < \omega \rbrace$ is countable and $\bigcup \lbrace K_i : i < \omega \rbrace \supseteq X$. For $\mathcal{P}$ to win, there must be an $x \in X$ such that for every neighborhood $U$ of $x$, $U$ hits infinitely many $p_n$, but$x \in U_m \subseteq K_m$ for some $n < \omega$ and $p_n \not\in K_m$ for $n \geq m$. So there is no such $x$ and $\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)$.
	\end{proof}

	\begin{theorem}
		$\boldsymbol{\mathcal{K}$ $\underset{pre}{\uparrow}$ $Gru_{\mathcal{K}, \mathcal{P}} (X)} \Rightarrow X$ is \textbf{hemicompact}.
	\end{theorem}
	\begin{proof}
		We prove the contrapositive. Let $\sigma$ be a predetermined strategy, and assume $X$ isn't hemicompact. So there exists a compact $K$ that isn't a union of finite $\sigma(n)$, so player $\mathcal{P}$ may always legally choose a point $p_n \in K$. Then by the lemma, $\langle p_n \rangle$ has a cluster point because for each $x \in K$ there is a $U_x$ that contains infinitely many $p_n$, and $\lbrace U_x : x \in K \rbrace$ covers $K$. Therefore $\sigma$ isn't a winning strategy.
	\end{proof}

\bibliographystyle{plain}
\bibliography{bib}

\end{document}
